The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-06 src/ms.tex
add more context to community infrastructure section
Add section author for community-oriented infrastructure
First draft of abstract

\begin{abstract}

    To be written...

\end{abstract}

@@

@@

@@

>>>>

\begin{abstract}
The \astropy Project supports and fosters the development of open-source and openly-developed
\python packages that provide commonly-needed functionality to the astronomical
community.
A key element of the \astropy Project is the core package \astropypkg, which serves as the
foundation for more specialized projects and packages.
In this article, we summarize key features in the core package as of the recent major
release, version 5.0, and provide major updates for the project.
We then discuss supporting a broader ecosystem of inter-operable packages,
including connections with several observatories and missions.
We also revisit the future outlook of the \astropy Project and the current
status of Learn Astropy. Last but not least, we contemplate the current
and future challenges facing the project.
\end{abstract}

@@

\secauthor{Adrian Price-Whelan}

@@

\secauthor{Nicholas Earl}

@@

This includes an overview of the sphinx-astropy tools, the pytest extensions
maintained by astropy, and the package template.
